---
title: "Final_Project"
author: "Kaden Pickering"
date: "3/21/2022"
output: html_document
---

```{r}
library(tidyverse) 

hockey_data <- read_csv("all_teams.csv") 
pittsburgh_penguins <- read_csv("Pittsburgh_data.csv") 
```

```{r}
all_situations <- hockey_data %>%
  filter(situation == "all") 

even_strength <- hockey_data %>%
  filter(situation == "5on5")

power_play <- hockey_data %>%
  filter(situation == "5on4")

short_handed <- hockey_data %>%
  filter(situation == "4on5")

other_situations <- hockey_data %>%
  filter(situation == "other") 
```

# Get the data set into a workable place that I can wrap my head around
```{r}
PP_all_situations <- pittsburgh_penguins %>%
  filter(situation == "all") 

PP_even_strength <- pittsburgh_penguins %>%
  filter(situation == "5on5")

PP_power_play <- pittsburgh_penguins %>%
  filter(situation == "5on4")

PP_short_handed <- pittsburgh_penguins %>%
  filter(situation == "4on5")

PP_other_situations <- pittsburgh_penguins %>%
  filter(situation == "other") 
```

# Start even smaller to get some perspective
```{r}
Pitt_2017 <- pittsburgh_penguins %>%
  filter(season == "2017") 
```

```{r}
PP_all_situations_small <- Pitt_2017 %>%
  filter(situation == "all") 

PP_even_strength_small <- Pitt_2017 %>%
  filter(situation == "5on5")

PP_power_play_small <- Pitt_2017 %>%
  filter(situation == "5on4")

PP_short_handed_small <- Pitt_2017 %>%
  filter(situation == "4on5")

PP_other_situations_small <- Pitt_2017 %>%
  filter(situation == "other")
```
# Still so many observations. Start with looking at just one situation (PowerPlay) 

# The more shots, the better chance of scoring on the powerplay...right? Let's see if that theory checks out. 
```{r}
library(tidyverse) 



 PP_shots <- PP_power_play_small %>%
  select(opposingTeam, shotAttemptsFor, shotsOnGoalFor, goalsFor, gameId) %>%
   mutate(propShotsThrough = shotsOnGoalFor / shotAttemptsFor) %>%
   rename(goalsFor = goalsFor) 

```


```{r}
shotsThrough_sub <- PP_shots %>% 
  filter(opposingTeam == "WSH")

 ggplot(shotsThrough_sub, aes(x = propShotsThrough, y = goalsFor)) +
  geom_point()
```


```{r}
library(shiny)

ui <- fluidPage(
  
  titlePanel("Do More Successful Shot Attempts Lead to More Goals on the PowerPlay?"), 
  
  sidebarLayout(sidebarPanel(
    selectizeInput("opponentchoice",
    label = "Choose an Opponent", choices = levels(factor(PP_shots$opposingTeam)),
    selected = "STL")),
                mainPanel(plotOutput("scatterplot"))
                )
  
)

server <- function(input, output, session) {
  
  shotsThrough_sub <- reactive({
    PP_shots %>% filter(opposingTeam == input$opponentchoice)
  })
  
  scatter_plot <- reactive({ 
    ggplot(shotsThrough_sub(), aes(x = goalsFor, y = propShotsThrough)) +
  geom_point() +
    theme_classic() + 
      labs(x = "Goals Scored on the PowerPlay", y = "Proportion of Shot Attempts On Net")
  })
  
  output$scatterplot <- renderPlot({
    scatter_plot()
  })
}

shinyApp(ui, server)
```

#Extra code for shiny 

 small_shotsThrough_sub <- reactive({
    shotsThrough_sub %>% filter(opposingTeam == input$gamechoice)
  })
  
  scatter_plot <- reactive({
    ggplot(small_shotsThrough_sub(), aes(x = .data[[input$varchoice]])) +
      geom_point()
  })
  
  output$scatterplot <- renderPlot({
    scatter_plot()
  })
  
  
  
  #radioButtons("varchoice", label = "Choose a Category",
                 #choices = var_choices),
                 
                 # var_choices <- names(PP_shots)[2:4]
                 
                 
  Tomorrow, 3/30, begin making second part of app with radio buttons to choose all situations of shots to see it on a wider scale for the 2017 pittsburgh penguins. Also, ask how to create a reactive table for each. 